Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis

### 2019-09-01 03_Preliminary_analysis.Rmd
Correct some graphs

# Which row spacing leads to the higher yeild potential
PM_MB_means %>%
   filter(Year >= 2017)%>%
#   filter(Fungicide == "control") %>%
ggplot(aes(y = as.numeric(grain_yield.t.ha.), x = row_spacing, colour = Location))+
   geom_jitter(width = 0.01)+
   geom_smooth()+
#   scale_y_continuous(limits = c(-5,15))+
   theme_usq()

@@

# plot table as a box plot
PM_MB_means %>%
   filter(Fungicide == c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" , "Amistar","Tebeconazole","propiconazole"))%>%
ggplot(aes(y = prop_YG, x = Fungicide))+
   geom_boxplot()+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   theme(axis.text.x = element_text(angle = 30, hjust =.51, vjust = 0.3))
   #scale_x_continuous(limits = c(-0.3,0.6))

@@

PM_MB_means %>%
   filter(total_Fungicide ==1 |total_Fungicide ==2 ) %>%
ggplot(aes(y = prop_YG, x = Fungicide))+
   facet_grid(cols = vars(total_Fungicide))+
   geom_boxplot(aes(fill = Fungicide, alpha = 0.5))+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
   #scale_x_continuous(limits = c(-0.3,0.6))

@@

```{r echo = FALSE, message=FALSE, warning=FALSE}
PM_MB_means %>%
   filter(Fungicide != "control") %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(
      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))

# What range of 
unique(PM_MB_means1$days_from_1st)
PM_MB_means1 %>%
   group_by(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))) %>%
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   kable(caption = "Difference in days between first sign of disease and first fungicide application and the effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

>>>>

# Which row spacing leads to the higher yeild potential
PM_MB_means %>%
   filter(Year >= 2017)%>%
#   filter(Fungicide == "control") %>%
ggplot(aes(y = as.numeric(grain_yield.t.ha.), x = row_spacing, colour = Location))+
   geom_smooth(method = "gam")+
   geom_jitter(width = 0.01)+
   #   scale_y_continuous(limits = c(-5,15))+
   theme_usq()

@@

# plot table as a box plot
PM_MB_means %>%
   filter(Fungicide == c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" , "Amistar","Tebeconazole","propiconazole"))%>%
ggplot(aes(y = prop_YG, x = Fungicide))+
   geom_boxplot()+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   coord_flip()
   #theme(axis.text.x = element_text(angle = 30, hjust =.6, vjust = 0.83))
   #scale_x_continuous(limits = c(-0.3,0.6))

@@

PM_MB_means %>%
   filter(total_Fungicide ==1 |total_Fungicide ==2) %>% 
   filter(Fungicide != "Pyrazophos" & Fungicide != "control" & Fungicide != "Benomyl" & Fungicide != "Acibenzolar-S-Methyl" & Fungicide != "200g/L azoxystrobin + 80 g/L cyproconazole + adj" ) %>%
ggplot(aes(y = prop_YG, x = Fungicide))+
   facet_grid(rows = vars(total_Fungicide))+
   geom_boxplot(aes(fill = Fungicide, alpha = 0.5))+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(y = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved\ngrouped by Fungicide type")+
   theme_usq()+
   theme(legend.position="none")+
   coord_cartesian()+
   scale_x_discrete(limits = c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin","propiconazole", "Tebeconazole", "200g/L azoxystrobin + 80 g/L cyproconazole", "Sulphur", "Carbendazim", "Pyraclostrobin","Amistar"))+
 #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
   coord_flip()
   #scale_x_continuous(limits = c(-0.3,0.6))

levels(PM_MB_means$Fungicide)

@@

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
PM_MB_means %>%
   filter(Fungicide != "control") %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(
      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))

```{r spray_timing&PropYield}
# What range of 
unique(PM_MB_means1$days_from_1st)
PM_MB_means1 %>%
   group_by(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))) %>%
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   kable(caption = "Difference in days between first sign of disease and first fungicide application and the effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)
